---
title: "assignment1-Yanbing Chen"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


car_viz.R
```{r}

library(tidyverse)

# call built-in data mtcars.
data(mtcars)

# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]


# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]

# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)

# Now use the function from hand_functions.R

sp_out <- sum_special(mtcars_mpg2)


# library(esquisse)
# 
# esquisser(data = mtcars_mpg2, viewer = "browser")



ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()


# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?


ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")
```


hand_functions.R
```{r}


sum_special <- function(df_x){
  
  ## sum_special calculates data summary statistics
  ## the input param df_x is the data frame of input values
  
  #  browser()  # browser() will start the debugger
               # if the line is uncommented
  
  
  ## test the input data to assure that it is a data frame.
  try(if(!is.data.frame(df_x)) stop("Input data must be a data frame."))
  
  
  sp_means <- apply(df_x, MARGIN = 2, FUN = mean)
  sp_var <- apply(df_x, MARGIN = 2, FUN = var)
  sp_cov <- cov(df_x)
  sp_cor <- cor(df_x)
  
  ## Note that defining a list with the 
  ## syntax list(list_name = list_content) produces
  ## named list items
  sp_outputs <- list(sp_means=sp_means, 
                     sp_var = sp_var, 
                     sp_cov = sp_cov, 
                     sp_cor = sp_cor)
  
  return(sp_outputs)
}
```


1.The text of the document should describe the data and discuss what you have learned in this very simple exploration.

Answer: From this homework, I learned how to connect github and R studio together to better share the project code. Based on this, in addition to learning more excellent codes, I think it will help us to improve our work's efficiency in our future work.
